Hardware-Accelerated Computation of Stellar Light Curves

### 2024-07-02 latex/paper.tex
starting proper perfomance workflow + gitignore generated data

\newpage
\section{starry}\label{starry}

@@

\subsection{Autodiff?}

@@

As described in \autoref{solution_vectors}, we compute \textit{starry} light curves using the Gauss Legendre quadrature to approximate the $\mathcal{P}$ integral involved in the expression of the solution vector $s_{n}$. Hence, the precision of the computed light curve depends on the order of the Legendre polynomial which defines the number of points used to approximate $\mathcal{P}$. For this reason, users must carefully set the order parameter to reach the precision required for their application, keeping in mind that a higher order leads to a longer computation time. In this section, we evaluate the performance of \texttt{jaxoplanet} against the C++ implementation of \texttt{starry}.\\\\
\autoref{fig:relative_error_1} shows the relative numerical error in the flux of a linearly limb-darkened star transited by an opaque companion of radius $r$ over a range of impact parameters $b$. Evaluated for different Legendre polynomial orders $n$, this figure shows the decrease of the relative error with the order of the Gauss-Legendre approximation.\\\\
At a fixed occultor radius, \autoref{fig:relative_error_2} shows the time required to compute the flux of the system for a range of $N$ impact parameters $b$, plotted against the maximum relative error reached, the order $n$ of the Gauss-Legendre approximation, and the hardware used for the computation.
\begin{figure}[H]
    \begin{center}
        \includegraphics[width=\textwidth]{../workflows/performance/relative_error_1.png}
        \caption{}
        \label{fig:relative_error_1}
    \end{center}
\end{figure}
\begin{figure}[H]
    \begin{center}
        \includegraphics[width=\textwidth]{../workflows/performance/relative_error_2.pdf}
        \caption{}
        \label{fig:relative_error_2}
    \end{center}
\end{figure}
These computations were run on an apple M1 CPU and an NVIDIA ... GPU. Thanks to the use of JAX, no harware-specific... \\\\

@@

\subsection{Speed}

>>>>

\newpage
\section{starry formalism}\label{starry}

@@

@@

As described in \autoref{solution_vectors}, we compute \textit{starry} light curves using the Gauss Legendre quadrature to approximate the $\mathcal{P}$ integral involved in the expression of the solution vector $s_{n}$. Hence, the precision of the computed light curve depends on the order of the Legendre polynomial which defines the number of points used to approximate $\mathcal{P}$. For this reason, users must carefully set the order parameter to reach the precision required for their application, keeping in mind that a higher order leads to a longer computation time. In this section, we evaluate the performance of \texttt{jaxoplanet} against the C++ implementation of \texttt{starry}.\\\\
\autoref{fig:relative_error_1} shows the relative numerical error in the flux of a linearly limb-darkened star transited by an opaque companion of radius $r$ over a range of impact parameters $b$. Evaluated for different Legendre polynomial orders $n$, this figure shows the decrease of the relative error with the order of the Gauss-Legendre approximation.\\\\
At a fixed occultor radius, \autoref{fig:relative_error_2} shows the time required to compute the flux of the system for a range of $N$ impact parameters $b$, plotted against the maximum relative error reached, the order $n$ of the Gauss-Legendre approximation, and the hardware used for the computation.
\begin{figure}[H]
    \begin{center}
        \includegraphics[width=\textwidth]{../workflows/performance/figures/error_n.png}
        \caption{}
        \label{fig:relative_error_1}
    \end{center}
\end{figure}
\begin{figure}[H]
    \begin{center}
        \includegraphics[width=\textwidth]{../workflows/performance/figures/time_n.pdf}
        \caption{}
        \label{fig:relative_error_2}
    \end{center}
\end{figure}
These computations were run on an apple M1 CPU and an NVIDIA ... GPU. Thanks to the use of JAX, no harware-specific... \\\\

@@
